Clicks and Cliques

### 2018-12-18 papersoul.Rnw
change code firstplot1 chunk, quantiles in x.axis labs

# to be removed...
#library(reshape2)
library(plyr)

# data wrangling
library(tidyverse)
library(stats)
library(car)

@@

soul.red2 <- soul.red2 %>%
  mutate(cl.id = factor(km$cluster) )

@@

\begin{figure}
<<firstplot1, dependson='data',echo=FALSE, fig.height=6, fig.keep='all', out.width='0.48\\linewidth',message=FALSE,warning=FALSE>>=

br <-  with(soul, quantile(OPENNESS, prob = seq(0,1, .2), na.rm = T))
soul$Openess <- with(soul, cut(OPENNESS, br))
levels(soul$Openess) <- round(br, 1)

br <-  with(soul,quantile(SOCIAL_O, prob = seq(0, 1, .2), na.rm = T))
soul$Social.Offering <- with(soul, cut(SOCIAL_O, br))
levels(soul$Social.Offering) <- round(br, 1)

>>>>

# to be removed...
library(reshape2)
library(plyr)

# data wrangling
library(magrittr)
library(tidyverse)
library(stats)
library(car)

@@

 soul.red2 %<>%
  mutate(cl.id = factor(km$cluster) )

@@

\begin{figure}
<<firstplot1, dependson='data',echo=FALSE, fig.height=6, fig.keep='all', out.width='0.48\\linewidth',message=FALSE,warning=FALSE>>=
 soul%<>% 
  mutate(Openess = cut(OPENNESS, breaks = quantile(OPENNESS, prob = seq(0,1, .2), na.rm = T), labels = c("Q1","Q2","Q3", "Q4", "Q5")), 
         Social.Offering = cut(SOCIAL_O, breaks = quantile(SOCIAL_O, prob = seq(0, 1, .2), na.rm = T), labels = c("Q1","Q2","Q3", "Q4", "Q5")))
